A seamless, client-centric programming model for type safe web applications

### 2014-06-19 paper.tex
Fix Remotable implementation.
Fix JS syntax highlighting.

\label{sec:jsexample}
\begin{listingfloat}
\begin{code}
function handshake(sock) {sock.send('helo');}
function chat(sock, msg) {sock.send('text' + msg);}

@@

  sock.onopen = function(e) {
    handshake(sock);
    msgbox.addEventListener('keydown', function(e) {
      if(e.keyCode == 13) {
        var msg = msgbox.value;
        msgbox.value = '';
        chat(msg);
      }
    });
  };
};
\end{code}
\caption{JavaScript chatbox implementation}
\label{lst:javascript-client}
\end{listingfloat}

@@

instance Serialize a => Remotable (Server a) where
  mkRemote m = fmap toJSON m

>>>>

\label{sec:jsexample}
\begin{listingfloat}
\begin{lstlisting}[language=JavaScript]
function handshake(sock) {sock.send('helo');}
function chat(sock, msg) {sock.send('text' + msg);}

@@

  sock.onopen = function(e) {
    handshake(sock);
    msgbox.addEventListener('keydown', function(e) {
      if(e.keyCode == 13) {
        var msg = msgbox.value;
        msgbox.value = '';
        chat(msg);
      }
    });
  };
};
\end{lstlisting}
\caption{JavaScript chatbox implementation}
\label{lst:javascript-client}
\end{listingfloat}

@@

instance Serialize a => Remotable (Server a) where
  mkRemote m = \_ -> fmap toJSON m
